### 2012-05-23 inst/examples/policycosts/L1.Rmd
include mean/sd data on induced and direct costs

``` {r policycost}
costs <- dt[ , sum(policy_cost), by=reps]
profits <-dt[ , sum(profit_fishing), by=reps]

@@

>>>>

These need to be discounted!

``` {r policycost}
costs <- dt[ , sum(policy_cost * (1-delta)^(time-1)), by=reps]
profits <-dt[ , sum(profit_fishing * (1-delta)^(time-1)), by=reps]

@@

## Results

Parameters have been chosen to achieve a 25% reduction in the net present value of the stock induced by the policy cost.
The net present value is 380.4 according the the exact calculation (see npv0 in [exact_npv.md](https://github.com/cboettig/pdg_control/blob/master/inst/examples/policycosts/exact_npv.md)) which looks close to the average in the stochastic realizations [baseline.md](https://github.com/cboettig/pdg_control/blob/master/inst/examples/policycosts/baseline.md).

```{r}
mean(profits$V1)
sd(profits$V1)
````

Compare these induced costs to the costs of actual adjustment.  Direct costs:

```{r}
mean(costs$V1)
sd(costs$V1)
````

Induced costs:

```{r}
380.4 - mean(profits$V1)
````

### 2012-05-23 inst/examples/policycosts/baseline.Rmd
include mean/sd data on induced and direct costs

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="L1/" or`

@@

# Policy Costs L1
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 1.52
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
````

@@

Parameters have been chosen to achieve a 25% reduction in the net present value of the stock induced by the policy cost.
The net present value is 380.4 according the the exact calculation (see npv0 in [exact_npv.md](https://github.com/cboettig/pdg_control/blob/master/inst/examples/policycosts/exact_npv.md)) which looks close to the average in the stochastic realizations [baseline.md](https://github.com/cboettig/pdg_control/blob/master/inst/examples/policycosts/baseline.md).

```{r}
mean(profits$V1)
sd(profits$V1)
````

Compare these induced costs to the costs of actual adjustment.  Direct costs:

```{r}
mean(costs$V1)
sd(costs$V1)
````

Induced costs:

```{r}
380.4 - mean(profits$V1)
````

>>>>

`ro fig.width=10, fig.height=7, message=FALSE, comment=NA, cache=TRUE, verbose=TRUE, cache.path="baseline/" or`

@@

# Baseline Policy Costs (no cost)
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r policycost_optim }
c2 <- 0 
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
````

@@

```{r }
mean(profits$V1)
sd(profits$V1)
````
